Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-02-27 Grassmannian_cells.tex
TeX cleanup

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively satisfying $\Hom(P_m,P_r)=0$ (resp. $\Hom(I_r,I_m)=0$) and $\Ext(P_r,P_m)=0 $ (resp. $\Ext(I_m,I_r)=0$) for $1\leq r\leq m$.
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.

@@

	  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable. As both, the isomorphism classes of indecomposables and the isomorphism classes of truncated projectives of dimension $d(m,r)$, are parametrized by the same Grassmannian, this gives the second claim.

As there exist representations with trivial endomorphism ring, the dimension vectors $d(m,r)$ are Schur roots.
%  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
  It follows that the set of indecomposable representations with trivial endomorphism ring forms a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
  This shows the last claim.
	\end{proof}
\begin{remark}
  There is a more elegant way to prove the first part of Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
  Actually, fixing the standard stability induced by the linear form $\Theta:\ZZ^{Q_0}\to\ZZ$ defined by $\Theta(d)=d_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
  We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
\end{remark}

@@

In the following, we say that $d:\supp(X)\to\ZZ$ satisfies the \emph{degree condition} for $X$ if it has the properties of Lemma~\ref{le:degree condition}.
\begin{theorem}
  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $X$.
  Then the torus action on $\bigoplus_{i\in Q_0} X_i$ induced by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
  A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced torus actions on the usual Grassmannian $\Gr_{\bfe_i}(X_i)$.
  By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
  which is equivalent to $U$ being liftable to the universal abelian covering.
\end{proof}
The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.\ to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$.
Now it is straightforward to check that there exist natural surjective morphisms $f_k:\widetilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k)}_0$ is a tree.
Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_i$ which induce a torus action on the quiver Grassmannian $\Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
If we denote the iterated torus fixed points by $\Gr^Q_\bfe(X)^{T^{(k)}}$, we obtain the following result.
\begin{corollary}
Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
  $$\Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} \Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr^{\hat Q^{(k)}}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
\end{corollary}
%\begin{corollary}
%  affine bundles over $\Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $\Gr^Q_\bfe(X)$ is smooth
%  \[\{U\in \Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
%\end{corollary}
Define the $F$-polynomial of a representation $X$ by 
$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))x^\bfe\in\ZZ[x_i\mid i\in Q_0].$$

@@

\begin{remark} Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}.\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,e)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,e)})$$
for $i=1,\ldots,n-1$. Recall that the representation $\tau\tilde P_3^{[k]}$ is given by 
\[ \xymatrix@R40pt@C10pt{&(1,e)&\\ (2,\alpha_1^{-1})\ar_{\alpha_1}[ru]&\cdots&(2,\alpha_{k}^{-1})\ar^{\alpha_{k}}[lu]}.\]
Note that the image of the homomorphism corresponding to the basis element spanning $$\Hom(\alpha_{k}^{(-1)}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)$$ corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$. This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$. In view of Lemma \ref{lem:2equivalence}, we forgo inserting the corresponding rectangles around the subquiver and just connect the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$. 
%In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.
\end{remark}
%It remains to consider the case when $m$ is even. Lemma \ref{AR} yields
%\begin{align}\label{eq:case2}
 %\Hom(P_{m-1},\tau \tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^{n}\Hom(\alpha_i\tilde P_{m-1},\tau \tilde P_{m}^{[k]})\cong \bigoplus_{i=k+1}^{n}\Ext(\tilde P_m^{[k]},\alpha_i\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
%\end{align}
Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $ \tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$. 
%This construction is motivated by considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}). 
%As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
%Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$.
Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $ P_{l}^{[j]}$ for $l\leq m$ and $j=0,\ldots, n-1$ and $l=m+1$ and $j=n-1,\ldots,k$. As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$. Moreover, we define $$\cQ_{m+1}^{[n-1]}:=\begin{cases}\alpha_{n}^{(-1)}.\cQ_{m}^{[1]}\text{ if }m\text{ is even}\\\alpha_{1}.\cQ_{m}^{[1]}\text{ if }m\text{ is odd}\end{cases}.$$

@@

\begin{theorem}\begin{enumerate}
\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe $ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe $ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
\end{enumerate}
\end{theorem}
\begin{proof}
The results of Section \ref{QG} imply that the second statement follows from the first one.
We proceed by induction on $m$ and $k$. The case of the representation $\tilde P_1$ is trivial. We have $(\tilde P_2^{[k]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the  subrepresentations are in one-to-one correspondence with the successor closed subsets of the quiver (\ref{coeff}) which is equivalent to  $\mathcal Q_2^{[k]}$ . Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[k]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[k]})=\{\pt\}$ if and only if $\tbfe\subset \mathcal Q_2^{[k]}$ is strong successor closed.

>>>>

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively satisfying $\Hom(P_m,P_r)=0$ (resp. $\Hom(I_r,I_m)=0$) and $\Ext(P_r,P_m)=0$ (resp. $\Ext(I_m,I_r)=0$) for $1\leq r\leq m$.
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.

@@

  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
  Since both the isomorphism classes of indecomposables and the isomorphism classes of truncated projectives of dimension $d(m,r)$ are parametrized by the same Grassmannian, this gives the second claim.

  As there exist representations with trivial endomorphism ring, the dimension vectors $d(m,r)$ are Schur roots.
  It follows that the set of indecomposable representations with trivial endomorphism ring forms a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
  This shows the last claim.
\end{proof}
\begin{remark}
  There is a more elegant way to prove the first part of Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
  Actually, fixing the standard stability induced by the linear form $\Theta:\ZZ^{Q_0}\to\ZZ$ defined by $\Theta(d)=d_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
  We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
\end{remark}

@@

In the following, we say that $d:\supp(X)\to\ZZ$ satisfies the \emph{degree condition} for $X$ if it has the properties of Lemma~\ref{le:degree condition}.
\begin{theorem}
  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $X$.
  Then the torus action on $\bigoplus_{i\in Q_0} X_i$ induced by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
  A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced torus actions on the usual Grassmannian $\Gr_{\bfe_i}(X_i)$.
  By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
  which is equivalent to $U$ being liftable to the universal abelian covering.
\end{proof}
The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.\ to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$.
Now it is straightforward to check that there exist natural surjective morphisms $f_k:\widetilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k)}_0$ is a tree.
Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_i$ which induce a torus action on the quiver Grassmannian $\Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
If we denote the iterated torus fixed points by $\Gr^Q_\bfe(X)^{T^{(k)}}$, we obtain the following result.
\begin{corollary}
Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
  $$\Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} \Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr^{\hat Q^{(k)}}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
\end{corollary}
%\begin{corollary}
%  affine bundles over $\Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $\Gr^Q_\bfe(X)$ is smooth
%  \[\{U\in \Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
%\end{corollary}
Define the $F$-polynomial of a representation $X$ by 
$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))x^\bfe\in\ZZ[x_i\mid i\in Q_0].$$

@@

\begin{remark} Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}.\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,e)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,e)})$$
for $i=1,\ldots,n-1$. Recall that the representation $\tau\tilde P_3^{[k]}$ is given by 
\[ \xymatrix@R40pt@C10pt{&(1,e)&\\ (2,\alpha_1^{-1})\ar_{\alpha_1}[ru]&\cdots&(2,\alpha_{k}^{-1})\ar^{\alpha_{k}}[lu]}.\]
Note that the image of the homomorphism corresponding to the basis element spanning $$\Hom(\alpha_{k}^{(-1)}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)$$ corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$. This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$. In view of Lemma \ref{lem:2equivalence}, we forgo inserting the corresponding rectangles around the subquiver and just connect the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$. 
%In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.
\end{remark}
%It remains to consider the case when $m$ is even. Lemma \ref{AR} yields
%\begin{align}\label{eq:case2}
 %\Hom(P_{m-1},\tau \tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^{n}\Hom(\alpha_i\tilde P_{m-1},\tau \tilde P_{m}^{[k]})\cong \bigoplus_{i=k+1}^{n}\Ext(\tilde P_m^{[k]},\alpha_i\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
%\end{align}
Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $\tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$. 
%This construction is motivated by considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}). 
%As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
%Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$.
Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $P_{l}^{[j]}$ for $l\leq m$ and $j=0,\ldots, n-1$ and $l=m+1$ and $j=n-1,\ldots,k$. As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$. Moreover, we define $$\cQ_{m+1}^{[n-1]}:=\begin{cases}\alpha_{n}^{(-1)}.\cQ_{m}^{[1]}\text{ if }m\text{ is even}\\\alpha_{1}.\cQ_{m}^{[1]}\text{ if }m\text{ is odd}\end{cases}.$$

@@

\begin{theorem}\begin{enumerate}
\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe$ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe$ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
\end{enumerate}
\end{theorem}
\begin{proof}
The results of Section \ref{QG} imply that the second statement follows from the first one.
We proceed by induction on $m$ and $k$. The case of the representation $\tilde P_1$ is trivial. We have $(\tilde P_2^{[k]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the  subrepresentations are in one-to-one correspondence with the successor closed subsets of the quiver (\ref{coeff}) which is equivalent to  $\mathcal Q_2^{[k]}$ . Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[k]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[k]})=\{\pt\}$ if and only if $\tbfe\subset \mathcal Q_2^{[k]}$ is strong successor closed.
